### 2019-05-25 draft.tex
added some text I won't use, but would like to keep
Added some text I won't use, but would like to keep. The text is after \end{document}.

>>>>

% In the context of physics, the word ``plasma'' is used to designate a gas whose degree
% of ionization is such that the interaction between its components is dominated by the electric
% and magnetic forces generated by the presence and movement of the negatively and positively
% charged particles.
%
% In the context of physics, the word ``plasma'' is used to designate a gas whose
% degree of ionization is such that its dynamics is dominated by the forces of
% electric and magnetic nature of the charged particles, overcoming the influence
% of the collisions between neutral particles.
%
% In the context of physics, the word ``plasma'' is used to designate a gas whose
% degree of ionization is such that the interactions involving forces of electric
% and magnetic nature of the charged particles, overcome the influence of the
% collisions between neutral particles, in the overall dynamics of the gas.
%
% In the context of physics, the word "plasma" designates a gas whose degree of
% ionization is such that the interactions involving forces of electric and magnetic
% nature, of the charged particles, overcome the influence of the neutral-neutral
% and neutral-charged binary collisions, on the overall dynamics of the gas. As a
% consequence of the long-range feature of the electric and magnetic fields, one
% charged particle may interact with several other particles, that interface with
% other charges, and so on; characterizing the so-called ``collective behavior''.
% Such behavior gives rise to a variety of plasma waves and instabilities, whose
% intensities will depend on another essential collective property of the plasma:
% the Debye shielding. The Debye shielding is defined as the resulting net charge
% inside a given volume element of the plasma. When the number of negative and
% positive particles are the same, the plasma waves and instabilities arise from
% the small fluctuations driven by the constant movement and interactions among the
% charges. These small fluctuations on the Debye shielding establish a fundamental
% characteristic of neutral plasmas, the ``quasineutrality''. On the other hand,
% plasmas that do not have overall charge neutrality might also have some degree
% of Debye shielding. In such case, however, the electric and magnetic fields are
% more intense and have a longer range due to the absence of quasineutrality.
% These characteristics make nonneutral plasmas a whole new subject, with distinct
% properties regarding its behavior and stability.
%
% A plasma is an ionized gas in which the charged particle population is sufficiently
% large so the forces of electric and magnetic nature, generated by the charges and
% their movement, overcome the influence of the collisions between neutral particles,
% that dominate the kinetics of neutral gases, on the overall dynamics of the system.
%

Let us consider a given set of atoms or molecules, which is composed of
positively and negatively charged particles, and also neutral components.
One can say, correctly, that such a system is an ionized gas, because of
the presence of charged particles in its composition. However, what can
be said about the dominant dynamics of the ionized gas, since neutral and
charged particles have quite a distinct behavior? The neutral particles,
assuming that the gravitational force is negligible, will move freely
in the medium until one collides with another \cite{klimon}. Therefore,
the interaction between the neutral components is characterized as
short-ranged, since it relies only on collisions between two particles.
Charged particles, on the other hand, are sources of electric fields.
Besides that, their motion generates currents that will induce magnetic
fields. The charged particles dynamics is dominated by the presence
of these fields that can act at distance, interacting and  the
fields of several particles at the same time.
